FIXME

### 2013-09-04 writeups/proposal/proposal.tex
foo
Former-commit-id: 296f58991ce633975436b826ebf1a182cc812e39 [formerly e00b42e5cc441d28f544568f233e49adb9004d66]
Former-commit-id: d81d8556e5955210777b145e1a967098030a04d9

RP used the simplest permutation possible to create a new environment vector.
Performance is actually better than BEAGLE.
Computational efficiency is better as well.
Strong case for using RP over circular convulation for decoding / encoding.
TODO: Summarize \cite{Recchia2010}

>>>>

Random permutations use one of simplest permutations possible to create a new environment vector.
This operation is much less costly than circular convoluation used by the BEAGLE model, which allows random permutations to scale better and handle larger datasets.
However, even though random permutations is a simpler representation than BEAGLE, it also performs better when trained on the same sized corpus.

\textcite{Recchia2010} found that random permutations could use smaller vectors to produce equivalent performance (better compression), and scale to larger datasets (better computational efficiency).
The vector x performance tradeoff was tested on a simple paired associative retrieval task. 
Retrieval accuracy for the vector-based models remained high even after reducing each environment vector's length from \num{2048} to \num{1024}.
This indicates that vector-based representations using random permutations compress better than those using circular convolution.

To test computational efficiency, each model was trained on a subset of the Wikipedia corpus, and tested on the TOEFFL (among other tasks).
The random-permutatino model was trained on \num{2.33} GB corpus.
The BEAGLE model was unable to train on a corpus this large, so both models were also trained on an additional \num{35} MB subset of the Wikipedia corpus.
The random permutatino model performed as well or slightly better than teh BEAGLE model when trained on the smaller corpus.
The model's performance also significantly improved when trained on the much larger corpus that was computationally intractable for the BEAGLE model.
These results make a strong case to favor random-permutations over circular convoluation when implementing vector-based memory representations.
